lifespan_eda

### 2024-02-17 eda/lifespan_eda.Rmd
quick edits

left_join(cn.df.eulerfilt, study_mad) %>%
  ggplot() +
  geom_boxplot(aes(x=study, y=surfholes)) +
  geom_point(aes(x=study, y=(study_euler_median+2*study_euler_madconst1)), color="red")
```

>>>>

# left_join(cn.df.eulerfilt, study_mad) %>%
#   ggplot() +
#   geom_boxplot(aes(x=study, y=surfholes)) +
#   geom_point(aes(x=study, y=(study_euler_median+2*study_euler_madconst1)), color="red")
```
